Next Generation Planning - Structuring and Sharing Environmental Drivers Data for the St. Lawrence System

### 2020-02-05 Submission/Beauchesne-eDriversMS.Rmd
commit all changes that were made for paper submission

---
title: Next Generation Planning - Structuring and Sharing Environmental Drivers Data for the St. Lawrence System
author: David Beauchesne^1,2,\*^, Rémi M. Daigle^2^, Steve Vissault^3^, Dominique Gravel^3^, Andréane Bastien^4^, Simon Bélanger^5^, Pascal Bernatchez^5^, Marjolaine Blais ^6^, Hugo Bourdages^6^, Clément Chion^7^, Peter S. Galbraith^6^, Benjamin Halpern^8,9^, Camille Lavoie^2^, Christopher W. McKindsey^6^, Alfonso Mucci^10^, Simon Pineault^11^, Michel Starr^6^, Anne-Sophie Ste-Marie^4^, Philippe Archambault^2^
fontsize: 12pt
font-family: Times New Roman
output:
  pdf_document:
    toc: false
    number_sections: true
  word_document:
    toc: false
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{listings}
   - \usepackage[svgnames]{xcolor}
   # - \usepackage{titling}
   # - \pretitle{\begin{flushleft}}
   # - \posttitle{\end{flushleft}}
   - \usepackage{lscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}
   - \usepackage{bbm}
   - \usepackage{float}
relativeurls: true
bibliography: eDriversMS.bib
csl: frontiers.csl
link-citations: yes
---

@@

\begin{figure}[H]
\centering
\includegraphics{./Figures/cluster.png}
\caption{Distribution of threat complexes in the Estuary and Gulf of St. Lawrence (upper panel). Threat complexes (a term coined by Bowler et al., 2019) are areas with similar cumulative driver exposure regimes. Mean intensity of all coastal (red), climate (green), fisheries (blue) and marine traffic (purple) drivers within each threat complex (lower panel). Refer to the Supplementary Materials for more details.}
\label{cluster}
\end{figure}

>>>>

---
title: Next Generation Planning - Structuring and Sharing Environmental Drivers Data for the St. Lawrence System
author: David Beauchesne^1,2,\*^, Rémi M. Daigle^2^, Steve Vissault^3^, Dominique Gravel^3^, Andréane Bastien^4^, Simon Bélanger^5^, Pascal Bernatchez^5^, Marjolaine Blais ^6^, Hugo Bourdages^6^, Clément Chion^7^, Peter S. Galbraith^6^, Benjamin Halpern^8,9^, Camille Lavoie^2^, Christopher W. McKindsey^6^, Alfonso Mucci^10^, Simon Pineault^11^, Michel Starr^6^, Anne-Sophie Ste-Marie^4^, Philippe Archambault^2^
fontsize: 12pt
font-family: Times New Roman
output:
  pdf_document:
    toc: false
    number_sections: true
    keep_tex: true
  word_document:
    toc: false
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{listings}
   - \usepackage[svgnames]{xcolor}
   # - \usepackage{titling}
   # - \pretitle{\begin{flushleft}}
   # - \posttitle{\end{flushleft}}
   - \usepackage{lscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}
   - \usepackage{bbm}
   - \usepackage{float}
relativeurls: true
bibliography: eDriversMS.bib
csl: frontiers.csl
link-citations: yes
---

@@

\begin{figure}[H]
\centering
\includegraphics{./Figures/cluster.png}
\caption{Distribution of threat complexes in the Estuary and Gulf of St. Lawrence (upper panel). Threat complexes (a term coined by Bowler et al., 2019) are areas with similar cumulative driver exposure regimes. Mean intensity of all coastal (red), climate (green), fisheries (blue) and marine traffic (purple) drivers within each threat complex (lower panel). Refer tp Table 1 for acronym meaning and to the Supplementary Materials for more details.}
\label{cluster}
\end{figure}
